---
title: "RF1_behavior"
author: "CNDS"
date: "June 12, 2019"
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
```

```{r load data, warning=FALSE, echo=FALSE}
setwd("~/Projects/RF1/")

nses <- 1
nblock <- 4
nmetrics <- length(c("CorrectTrials","#0back","#2back","acc0back","acc2back","avgRT0back","avgRT2back"))

sumtbl <- matrix(0, nrow = (nses*nblock),ncol = nmetrics)

file_ct = 1
for (i_file in list.files(path = "~/Projects/RF1/")) {
  #df <- readLines(i_file) #nback_test_5_5-C412-21_numeric.csv
  #df <- df[-1] # remove first line (file path)
  #df <- df[-1] # remove second line (this data contains editted... comment)
  df <- read.csv(file = i_file, header = TRUE, stringsAsFactors = FALSE)
  
  # compute multi-visit accuracy
  trials <- which(df$CorrectResp != 'NA')
  df <- df[trials,]
  
  df.correct <- df[which(df$NBackImage1.RESP | df$NBackImage2.RESP == df$CorrectResp),]
    sumtbl[file_ct,1] <- nrow(df.correct) # number of correct trials
    sumtbl[file_ct,2] <- sum(df.correct$NbackLevel == 1) # number of correct, 0-back trials
    sumtbl[file_ct,3] <- sum(df.correct$NbackLevel == 2) # number of correct, 2-back trials
    
    sumtbl[file_ct,4] <- sum(df.correct$NbackLevel == 1)/sum(df$NbackLevel == 1) #acc_0back
    sumtbl[file_ct,5] <- sum(df.correct$NbackLevel == 2)/sum(df$NbackLevel == 2) #acc_2back
  
  # compute multi-visit reaction times  
      a <- which(df.correct$NBackImage2.RT != 0)
      for (i_trial in a) {
        df.correct$NBackImage2.RT[i_trial] <- df.correct$NBackImage2.RT[i_trial]+250
      }
      tot_RTtime <- df.correct$NBackImage1.RT + df.correct$NBackImage2.RT
    sumtbl[file_ct,6] <- mean(subset(tot_RTtime,df.correct$NbackLevel == 1)) #avgRT_0back
    sumtbl[file_ct,7] <- mean(subset(tot_RTtime,df.correct$NbackLevel == 2)) #avgRT_2back
    
    file_ct = file_ct+1
}

  
```

# Data Table (legend below)
```{r table, echo=FALSE}

df.sumtbl <- as.data.frame(sumtbl) #row.names = c("Ses1_Blk1","Ses1_Blk2","Ses2_Blk1","Ses2_Blk2")
colnames(df.sumtbl) <- c("trialscorr","trials0corr","trials2corr","ACC0Back","ACC2Back","avgRT0back","avgRT2back")
Name <- c("Ses1_Blk1","Ses1_Blk2","Ses2_Blk1","Ses2_Blk2")
df.sumtbl2 <- data.frame(Name,df.sumtbl)
if ( file_ct < 4 ) {
  df.sumtbl2[3:4,2:8] <- NA
}

#print(df.sumtbl)
#knitr::kable(df.sumtbl, format="markdown")
knitr::kable(df.sumtbl2, format="markdown")

```
  * trialscorr = number of trials correct
  * trials0corr = number of trials correct, in 0-back condition
  * trials2corr = number of trials correct, in 2-back condition
  * ACC0back = task accuracy, in 0-back condition
  * ACC2back = task accuracy, in 2-back condition
  * avgRT0back = average Reaction Time (RT), in 0-back condition
  * avgRT2back = average Reaction Time (RT), in 2-back condition

# Plots
```{r plots, echo=FALSE}
# Accuracy, filtered by NbackLevel (0 or 2)
ggplot(df.sumtbl) + geom_point(data = df.sumtbl,aes(x=rownames(df.sumtbl),y=ACC0Back,color = "0Back")) + geom_point(data = df.sumtbl,aes(x=rownames(df.sumtbl),y=ACC2Back,color = "2Back")) + labs(title="RF1 C263, Nback Accuracy", x="Visit", y="Accuracy", color="Nback:") + ylim(0,1) + geom_hline(yintercept=0.25, linetype="dashed")

# RT, filtered by NbackLevel (0 or 2)
ggplot(df.sumtbl) + geom_point(data = df.sumtbl,aes(x=rownames(df.sumtbl),y=avgRT0back,color = "0Back")) + geom_point(data = df.sumtbl,aes(x=rownames(df.sumtbl),y=avgRT2back,color = "2Back")) + labs(title="RF1 C263, avgRT on Correct Trials", x="Visit", y="RT", color="Nback:")

```

```{r evaluating effect of tms stim, echo=FALSE}

setwd("~/Projects/RF1/")

file_ct=1
ct=1
for (i_file in list.files(path = "~/Projects/RF1/C263/numeric")) {
  df <- read.csv(file = i_file, header = TRUE, stringsAsFactors = FALSE)

  # compute multi-visit accuracy
  trials <- which(df$CorrectResp != 'NA')
  df <- df[trials,]
  
  # create summary columns
  TrialCount <- rep(0,nrow(df));
  NBackImageAll.RESP <- rep(0,nrow(df));
  NBackImageAll.RT <- rep(0,nrow(df));
  NBackImageAll.ACC <- rep(0,nrow(df));
  # fill summary columns
  #ct=1
  for (i_trial in 1:nrow(df)) {
  if (!is.na(df$NBackImage1.RESP[i_trial])) {
      NBackImageAll.RESP[i_trial] <- df$NBackImage1.RESP[i_trial]
      NBackImageAll.RT[i_trial] <- df$NBackImage1.RT[i_trial]
    } else if (!is.na(df$NBackImage2.RESP[i_trial])) {
      NBackImageAll.RESP[i_trial] <- df$NBackImage2.RESP[i_trial]
      NBackImageAll.RT[i_trial] <- df$NBackImage2.RT[i_trial]+250 #NBackImage2 logged 250ms after NbackImage1 (ie t0)
    }
  
  if (NBackImageAll.RESP[i_trial] == df$CorrectResp[i_trial]) {
    NBackImageAll.ACC[i_trial] = 1
    } else {
      NBackImageAll.ACC[i_trial] = 0
    }
    
  TrialCount[i_trial] = ct
  ct=ct+1
  
  }
  # add columns to data
  df.updated <- data.frame(df,TrialCount,NBackImageAll.RESP,NBackImageAll.RT,NBackImageAll.ACC)
  if (ct == 301 & file_ct == 1) {
    df2 <- df.updated
  }
  file_ct=file_ct+1
}

df_final <- rbind(df2,df.updated)
```
## ses-tms1 visit, all trials
Dashed line seperates before (left, first 300) and after (right, last 300) iTBS stimulation
```{r plotting effect of tms stim, echo=FALSE}  
  ## plot1
  ggplot(df_final, aes(x=TrialCount, y=NBackImageAll.RESP, color=NBackImageAll.ACC)) + geom_point(size = 2) + labs(title="Response x Trial, by Accuracy", x="Trials", y="Response", color="Accuracy:") + geom_vline(xintercept=300, linetype="solid") + geom_vline(xintercept=150, linetype="dashed") + geom_vline(xintercept=450, linetype="dashed")
  ## plot2
  ggplot(df_final, aes(x=TrialCount, y=TMSStim, color=NBackImageAll.ACC)) + geom_point(size = 2) + labs(title="TMS Stim x Trial, colored by Accuracy", x="Trials", y="TMS: on (0) or off (1)", color="Accuracy:") + geom_vline(xintercept=300, linetype="solid") + geom_vline(xintercept=150, linetype="dashed") + geom_vline(xintercept=450, linetype="dashed")
  ## plot3
  ggplot(df_final, aes(x=TrialCount, y=NBackImageAll.RT, color=TMSStim)) + geom_point(size = 2) + labs(title="RT x Trial, by TMSStim", x="Trials", y="Reaction Time", color="TMSStim on/off:") + geom_vline(xintercept=300, linetype="solid") + geom_vline(xintercept=150, linetype="dashed") + geom_vline(xintercept=450, linetype="dashed")
  ## plot4
  ggplot(df_final, aes(x=TrialCount, y=NBackImageAll.RT, color=NBackImageAll.ACC)) + geom_point(size = 2) + labs(title="RT x Trial, by Accuracy", x="Trials", y="Reaction Time", color="Accuracy:") + geom_vline(xintercept=300, linetype="solid") + geom_vline(xintercept=150, linetype="dashed") + geom_vline(xintercept=450, linetype="dashed")
  


```

